\section{Summary}

In this work, the Quantum Hall Effect (QHE) was investigated in a two-dimensional electron system 
at low temperatures and high magnetic fields. 
The QHE provides a precise method to measure the ratio of Planck's constant $h$ to the elementary charge $e$,
leading to the determination of the von Klitzing constant $R_\text{K}$. Our measurements confirm the 
quantization of the Hall resistivity $\rho_\text{xy}$ in multiples of $h/e^2$, with the experimentally 
determined $R_\text{K}$ values agreeing with the exact value of $R_\text{K, exact} = \csname Klitzing1.4K\endcsname\,\text{k}\Omega$ 
within experimental uncertainties.
The charge carrier density $n$ was determined using three different methods: 
the classical Hall effect, the quantum Hall plateaus, and the Shubnikov-de Haas oscillations. 
The results were consistent across methods, with $n$ values in the range of $\csname nEins1.4K\endcsname \cdot 10^{15}\,\text{m}^{-2}$, 
showing a slight temperature dependence.
The cyclotron mass $m_\text{c}$ was calculated from the temperature dependence 
of the oscillation amplitudes in the longitudinal conductivity $\sigma_\text{xx}$. 
The determined values, $m_\text{c} = (\csname cyclotron15\endcsname)\cdot 10^{-2}m_\text{e}$ for the $1.4\,\text{K}$ and $3\,\text{K}$ 
pair and $m_\text{c} = (\csname cyclotron21\endcsname)\cdot 10^{-2}m_\text{e}$ for the $2.1\,\text{K}$ and $4.2\,\text{K}$ pair, 
are in good agreement with literature values.
Additionally, the Fermi wave vector $k_\text{F}$, Fermi energy $E_\text{F}$, and Fermi velocity $v_\text{F}$ 
were calculated assuming a parabolic energy dispersion. For $T = 4.2\,\text{K}$, 
the results were $k_\text{F} = (\csname kFermi4.2K\endcsname) \cdot 10^{8}\,\text{m}^{-1}$, $E_\text{F} = (\csname EFermi4.2K\endcsname)\cdot 10^{-2}\,\text{eV}$, 
and $v_\text{F} = (\csname vFermi4.2K\endcsname) \cdot 10^{5}\,\text{m/s}$. 
These values highlight the low-energy nature of the system and the necessity of 
low temperatures to maintain the two-dimensional confinement.
No evidence of the fractional Quantum Hall Effect (FQHE) was observed in the accessible magnetic field range. 
The absence of fractional plateaus and corresponding longitudinal resistivity peaks suggests that higher magnetic 
fields are required to observe this phenomenon.
In conclusion, the experimental results confirm the fundamental properties of the Quantum Hall Effect 
and provide insights into the electronic properties of the system, including charge carrier density, 
cyclotron mass, and Fermi parameters. The findings are consistent with theoretical predictions and 
highlight the precision of the QHE as a tool for fundamental physics and metrology.
